`make.events`

### 2023-02-27 inst/gitbook/01_getting_started.Rmd
Update 01_getting_started.Rmd
Compiles OK

---
title: "Getting start"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

@@

# Getting started

@@

> Note that here it is not necessary to specify `speciation = 1` since this is the default option, you can always just change the parameter of interest (e.g. changing `extinction = 0` to `extinction = 1/3`). However, we think it's good practice to attribute both parameters specifically to avoid any confusion.

>>>>

---
title: "Getting start"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../references.bib]
output:
  html_document: default
  pdf_document: default
---

@@

# Getting started {#gettingstarted}

@@

> Note that here it is not necessary to specify `speciation = 1` since this is the default option, you can always just change the parameter of interest (e.g. changing `extinction = 0` to `extinction = 1/3`). However, we think it's good practice to attribute both parameters specifically to avoid any confusion.
You can find more information about setting up more complex birth death parameters [in this section](#makebdparams).

### 2023-02-27 inst/gitbook/02_make.traits.Rmd
Compiles OK

---
title: "`make.traits`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

@@

```{r, echo = FALSE}
set.seed(123)
```

>>>>

---
title: "`make.traits`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../references.bib]
output:
  html_document: default
  pdf_document: default
---

@@

```{r, echo = FALSE}
library(dads)
set.seed(123)
```

### 2023-02-27 inst/gitbook/03_make.modifiers.Rmd
Compiles OK

---
title: "`make.modifiers`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "`make.modifiers`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../references.bib]
output:
  html_document: default
  pdf_document: default
---

### 2023-02-27 inst/gitbook/04_make.events.Rmd
Compiles OK

---
title: "`make.events`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "`make.events`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../references.bib]
output:
  html_document: default
  pdf_document: default
---

### 2023-02-27 inst/gitbook/05_other_functionalities.Rmd
Update 05_other_functionalities.Rmd
Compiles OK

---
title: "`make.events`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

```{r, echo = FALSE}
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```

@@

```{r}
## Making the speciation sampling always positive
make.bd.params(speciation = rnorm, absolute = TRUE)
## This is effectively making the speciation distribution equal to
make.bd.params(speciation = function(x) abs(rnorm(x)))
```

@@

## `drop.things`

>>>>

---
title: "`make.events`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../references.bib]
output:
  html_document: default
  pdf_document: default
---

```{r, echo = FALSE}
library(dads)
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```

@@

```{r}
## Making the speciation sampling always positive
make.bd.params(speciation = rnorm, absolute = TRUE)
```

@@

## `drop.things` {#dropthings}
